Appendix A

### 2020-10-04 appendixA/appendixA.Rmd
parameter plots have population line

  prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    facet_grid(dist~param, switch = "y") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "Estimate") +
    theme(legend.position = "none")
}

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params()

nice_prms %>% 
  filter(., dist == "Gamma" & data == "POP") %>% 
  plot_params()

>>>>

  title <- paste(dist, param)

  prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "Estimate") +
    theme(legend.position = "none")
}

prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    facet_grid(dist~param, switch = "y", scales = "free_y") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "Estimate") +
    theme(legend.position = "none")

prms.df %>% 
  mutate(fit.param = paste(dist, param)) %>% 
  ggplot(., aes(x = data, y = estimate, color = dist)) +
  facet_wrap(~fit.param, scales = "free_y") +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
  theme(legend.position = "none")
